%!TEX program=xelatex+makeindex+bibtex
\documentclass[final]{scrreprt} %scrreprt of scrartcl
\input{../../library/preamble.tex}
\input{../../library/style.tex}
\addbibresource{../../library/bibliography.bib}

\begin{document}

\section{Labday 5: Localization using TDOA information}
\label{ch:labday5}
\subsection{Report 6}
\subsubsection{Basic localization}
We assumned before doing the TDOA estimation that the delay between sending and receiving in the audio buffer is known, ASIO provides a helpful function getLatencies for that, this function gives you the input and output delays in samples.
The delay time is mostly dependent on sampling frequency and buffer size.
When the full delays are known the calculation becomes a lot easier since it can be solved using two microphones only.
\\ \\
Figure \ref{fig:location} shows how the location of the car can be found when the locations of the microphones (and thus the distance between them, $a_1 + a_2$) and the time between transmission and arrivals at the two microphones $t_1$ and $t_2$, which can be converted into a distance using the speed of sound $c = 340~m/s$.
Using this information, two possible locations can be found, the real location of the car and its mirrored version as shown in Figure \ref{fig:location}.

\begin{figure} [H]
\centering
	\begin{tikzpicture}	
		\node [anchor=east] at (0,0) (mic1) {Mic 1};
		\node [anchor=west] at (9,0) (mic2) {Mic 2};
		\node [anchor=south] at (6,3) (car) {Beacon};
		\node [anchor=north] at (4.5,-0.25) (a) {$a$};

		\draw (0,0) -- node[below]{$a_1$} (6,0)
			-- node[left]{$x$} (6,3)
			-- node[above, sloped]{$t_1 c$} (0,0);

		\draw (6,0) -- node[below]{$a_2$} (9,0)
			--  node[above, sloped]{$t_2 c$} (6,3);

		\draw [dotted] (0,0) -- (6,0)
			-- (6,-3)
			-- (0,0);

		\draw [dotted] (6,0) -- (9,0)
			--  (6,-3);
	\end{tikzpicture}
	\caption{Location determination.}
	\label{fig:location}
\end{figure}

From Figure \ref{fig:location}, equation \ref{eq:a1} and \label{eq:x} can be derived.
\begin{equation}
	a_1 = \frac{t_1^2 c^2 - t_2^2 c^2 + a^2}{2 a}
\label{eq:a1}
\end{equation}

\begin{equation}
	x = \sqrt{t_1^2 c^2 - a_1^2}
	\label{eq:x}
\end{equation}

To find the exact location of the beacon on the field when Mic 1 and Mic 2 are not on the same y-coordinate, an angular translation is needed as illustrated in Figure \ref{fig:angular-translation}.

\begin{figure} [H]
\centering
	\begin{tikzpicture}	
		\node [anchor=east] at (0,0) (mic1) {Mic 1};
		\node [anchor=south east] at (2.1213,6.3439) (car) {Beacon};
		\node [anchor=south west] at (1,0.15) {$\theta$};

		\draw [-*] (0,0) -- node[below]{$a_1$} (6,0)
			-- node[left]{$x$} (6,3);

		\draw [dashed, -*] (0,0) -- (4.2426,4.2426)
			-- (2.1213,6.3439);

		\draw [->] (1,0) arc (0:45:1);
	\end{tikzpicture}
	\caption{Angular translation.}
	\label{fig:angular-translation}
\end{figure}

\begin{equation}
	\theta = -\arctan{\frac{\text{Mic 2}_y - \text{Mic 1}_y}{\text{Mic 2}_x - \text{Mic 1}_x}}
	\label{eq:theta}
\end{equation}
Where $\theta$ is the angle between the two microphones.

The beacon location in x- and y-coordinates is found by adding the point ($a_1$, $x$) with an angular translation of $\theta$ to the location of Mic 1.
\\ \\
Since five microphones will be used instead of just two, the mirrored versions can be filtered out, leaving only the real location of the car as a solution.
By using only two microphones per location estimation instead of all five at once, wrong arrival times can be filtered out easily.
However, the arrival times are subject to errors, it might not be possible to filter the mirror images completely out of the solution sets.

\subsubsection{Height correction}
The height difference between the audio beacon and the microphones causes a larger time delay than expected when looking at the 2D plane.
However, this time delay can be corrected using Pythagoras' theorem (Equation \ref{eq:pythagoras}).

\begin{equation}
	t_{2D} = \sqrt{t_{3D}^2 - \Delta h^2}
	\label{eq:pythagoras}
\end{equation}

Where $\Delta h$ is the height difference between the beacon and the microphone.
The resulting $t_{2D}$ can be used in the basic localization to calculate the beacon location, independent of the height difference.

\subsubsection{TDOA to arrival times}
In order to use the TDOA data in the algorithm mentioned above, the time delays between the transmission and reception of the signal per microphone must be calculated from the TDOA data.
For this, it is known that this transition from TDOA to time delays is accomplished by adding a the same time constant time difference per microphone.
This constant is defined as the time difference between the absolute time of transmission and the absolute start time of the sample data, e.g. the absolute time of sample number one.
\\ \\
To find this constant, an orthogonal base of three microphones is used as in Figure \ref{fig:constant}.

\begin{figure} [H]
\centering
	\begin{tikzpicture}	
		\node [anchor=east] at (0,0) (mic1) {Mic 1};
		\node [anchor=west] at (9,0) (mic2) {Mic 2};
		\node [anchor=east] at (0,5) (mic1) {Mic 3};
		\node [anchor=south west] at (6,3) (car) {Beacon};

		\draw (0,0) -- node[below]{$x$} (6,0)
			-- node[left]{$y$} (6,3)
			-- node[above, sloped]{$t_1 c$} (0,0);

		\draw (6,0) -- node[below]{$B - x$} (9,0)
			--  node[above, sloped]{$t_2 c$} (6,3);

		\draw (0,0) -- node[left]{$y$} (0,3);

		\draw (0,3) -- node[left]{$H - y$} (0,5)
			-- node[above]{$t_3 c$} (6,3)
			-- node[below]{$x$} (0,3);

		\draw (0.5,0) -- (0.5,0.5) -- (0,0.5);
		\draw (5.5,0) -- (5.5,0.5) -- (6,0.5);
		\draw (0,2.5) -- (0.5,2.5) -- (0.5,3);
	\end{tikzpicture}
	\caption{Model used for determination of the constant time error.}
	\label{fig:constant}
\end{figure}

Using the formula of the altitude of a triangle, e.g. $y$ in triangle (Mic 1, Mic 2, Beacon), the altitude is defined in equation \ref{eq:y1}.

\begin{equation}
	y = \frac{2 \sqrt{s(s - B)(s - D_1)(s - D_2)}}{B}
\label{eq:y1}
\end{equation}

With $B$ the base of the triangle, $D_1$ and $D_2$ the other two sides of the triangle and $s$ half of the perimeter of the triangle, $s = (B + D_1 + D_2) / 2$.
In the case of triangle (Mic 1, Mic 2, Beacon) with altitude line $y$, the base $B = \lVert Mic 1 - Mic 2 \rVert$ and the other two sides as $D_1 = t_1 c$ and $D_2 = t_2 c$ or vice versa.
\\ \\
For triangle (Mic 1, Mic 3, Beacon), $y$ is defined in equation \ref{eq:y2}.

\begin{equation}
	y = \frac{t_1^2 c^2 - t_3^2 c^2 + H^2}{2 B}
\label{eq:y2}
\end{equation}

The parameters $t_1$, $t_2$ and $t_3$ are defined with an offset of the constant we wish to find.
Using Equation \ref{eq:y1} and \ref{eq:y2}, which define the same $y$ since the three microphones form an orthogonal basis, and having an offset on $t_1$, $t_2$ and $t_3$, Matlab solved the formula of the constant using the script report6-2.m (Listing \ref{lst:report6-2.m}) from Appendix \ref{app:source}.
\\ \\
Now that the constant is known, the algorithm using two microphones and the arrival times can be applied.
It must be noted that the height difference between the microphones and the beacon is not considered in the calculation of the constant time offset.
Matlab could not find an explicit solution for the 3D situation, hence it was not included.
This will lead to an error in the resulting location.
However, the error will be very small when the beacon is not close to the microphone, hence only one microphone will be compromised at once.
For that, the base of orthogonal microphones shift to all four possible combinations and check for the best basis with the smallest standard deviation between the resulting locations, so the most tightly grouped solutions.
\\ \\
The final Matlab script can be found in Appendix \ref{app:source} Listing \ref{lst:location.m} location.m, which implements everything discussed so far in this chapter.

\subsubsection{Testing}
The test script location-errors.m as found in Appendix \ref{app:source} Listing \ref{lst:location.m} was used to find the error mean, standard deviation and maximum.
The first test was in 2D mode; all microphones and the beacon were on the same height.
\\ \\
The other tests were with the four surrounding microphones 10 cm higher than the beacon and the last microphone 65 cm higher than the beacon.
The five microphones were set up as in the five microphone test setting from Labday 5.
All tests were done by calculating 2.500 points linearly spread on the 2.9m x 2.9m field.
The results are displayed in Table \ref{tab:errors}.

\begin{table} [H]
\centering
	\begin{tabular}{ c | c | c | c }
  	Setup & Error mean (mm) & Error standard deviation (mm) & Max error (mm) \\ \hline
  	2D & 0 & 0 & 0 \\
  	3D without height correction & 31.2 & 10.9 & 61.8 \\
	3D with height correction & 3.4 & 2.4 & 13.6 \\
	\end{tabular}
\caption{Location error details for different setups.}
\label{tab:errors}
\end{table}

The accuracy of the algorithm is sufficient, since the error mean and maximum are below $\SI{1}{\centi\meter}$.
A higher accuracy is not needed because other factors have a much bigger impact on the control of the car.
The height correction definitely adds accuracy to the location estimation as expected, hence it will be used later on.
This is however when the TDOA information is nearly infinitely accurate, which will not be the case.
The algorithm can give some erratic results when the measured time differences erroneous.
To prevent these erratic results to disrupt the workings of the final system we will have to use for example a moving average filter for the position.
The car has a certain maximum distance it can move per time unit. We will use that knowledge to make sure the positions are not ``faulty'' of invalid.

\end{document}